---
title: "the Central Limit Theorem meets exponential distribution"
author: "Vv"
date: "05/22/2015"
output: pdf_document
---
N.B.: issue "apt-get install lmodern" command to make pdf output available.

The Central Limit Theorem (CLT) is one of the most important theorems in statistics.
For our purposes, the CLT states that the distribution of averages of iid variables, properly normalized, becomes that of a standard normal as the sample size increases.
To be more formal:
$$\frac{\bar X_n - \mu}{\sigma / \sqrt{n}} =
    \frac{\mbox{Estimate} - \mbox{Mean of estimate}}{\mbox{Std. Err. of estimate}}
$$
where:  
$\bar X_n$ - sample average  
$\mu$      - mean of population  
$\sigma$   - standard deviation of population  
To be less formal:  
distribution of averages becomes estimator of original distribution.

Let's apply CLT to exponential distribution.  
The mean of exponential distribution is 1/lambda and the standard deviation is also 1/lambda.

In theory, distribution of the mean of n exponentials have following properties:  
1. mean (approximately) equal to $\mu$ of original population given n is big enough (n=$\infty$ always welcome)  
2. variance equal to $\sigma^2 / n$ (i.e. Standard Deviation/Error equal to $\sigma / \sqrt{n}$) of original population  
3. approximately normal
```{r, echo=FALSE}
    nCoeff          <- 40;
    nSim            <- 1000;
    lambda          <- 0.2;    
    populationMean  <- 1 / lambda;
    populationSD    <- 1 / lambda;
    sampleSD        <- populationSD / sqrt(nCoeff);
    sampleVariance  <- populationSD ^ 2 / nCoeff;
```
So expected mean and variance(standard deviation) are `r populationMean` and `r sampleVariance`(`r sampleSD`) respectivaley given n = `r nCoeff`.

```{r setoptions,echo=TRUE}
    options(scipen = 6, digits = 2);
```